Ants-Review: A Protocol For Open Anonymous Peer-Reviews

### 2020-06-07 paper-v1.tex
introducing the problem

\begin{document}
%
\title{Ants-Review: A Protocol For Open Anonymous Peer-Reviews}
%
%\titlerunning{Abbreviated paper title}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{Bianca Trovò\inst{1,2}\orcidID{0000-0002-6776-2304}\thanks{Correspondent author: bianca.trovo@alumni.unitn.it} \and
Nazzareno Massari\inst{3,4}\orcidID{0000-0002-6638-2174}}
%
\authorrunning{B. Trovò et N. Massari}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{Sorbonne Université, Faculté des Sciences et Ingénierie, 75005 Paris, France \and
Neurospin research center, CEA/SAC/DSV/I2BM, 91191 Gif-sur-Yvette, France
\email{bianca.trovo@alumni.unitn.it}\\
\and
Alma Mater Politecnico di Torino, 10129 Turin, Italy\and
Independent Blockchain Engineer, London, UK \\
\email{nazzareno@nazzarenomassari.com}}
%
\maketitle              % typeset the header of the contribution
%
\begin{abstract}
Peer-review is a necessary and essential quality control step for scientific publications. However, the process, which is very costly in terms of time investment, not only is not remunerated but it’s also not recognized by the academic community as a relevant scientific output for a researcher. Therefore, scientific dissemination is affected. Here, to solve this issue we propose a blockchain-based incentive protocol that rewards scientists also for their contributions to other scientists’ work and that builds up a reputational system. We designed a basic Bounty-like contract called AntsReview that allows any author to issue a call for peer-reviewing their scientific publication. If requirements are met, peer-reviews will be audited by an external editor and payed by the Issuer. To promote ethical behaviour the system will implement a quadratic funding on AntsReview.
\keywords{Blockchain  \and Open Science \and Peer-review \and Incentivization.}
\end{abstract}
%
%
\section{Introduction}
From its birth in 2008 as a distributed ledger for the peer-to-peer electronic cash system 'Bitcoin' \cite{Bitcoin}, blockchain technology has spread far beyond the sole cryptocurrency domain, in particular after the implementation of a general purpose smart contract functionality introduced by Ethereum. 
Besides a growing number of applications ranging from business, healthcare, music industry, government, identity to cite but a few, blockchain technology has recently started to catalyse the attention of the scientific community as well \cite{Bitcoin-Nature-focus,vanRossum2017-DigSci} with the promising potential of being a 'game changer' in outdated and broken scientific practices and leading towards Open Science \cite{AES}. In particular, a 'blockchainified science'\cite{BlockchainforScience} could 'reduce waste'\cite{ReducingWaste-Lancet}, by disclosing each step the research cycle to 'scientific self-correction' way before the final publication step and therefore help fixing the current reproducibility crisis in science. Scholars have pointed out how the intrinsic characteristics of blockchain technology (decentralization, for which there are no trusted third parties; cryptographic hashing, that creates a digital footprint able to keep a 'trail of research';  
to prevent vs publication bias (reporting only positive results) or p-hacking or ex-post-facto hypothesizing (changing the hypothesis after having looked into the data)

@@

\subsection{Ideas here}

@@

AntsReviewRoles[\ref{appendix:a}], to ensure integrity of the system, implements an access management, leveraging on AccessControl.sol by OpenZeppelin Library \cite{OZ}, through the creation of the Roles Issuer and Peer-Reviewer.
\newline It also integrates a circuit breaker design pattern via Pausable.sol by OpenZeppelin to allow the Pauser Role, that by default is the Owner of the Smart Contracts, to pause (or unpause) the functions in case of emergency.
\newline In this way, only the Issuer (author) can create a new AntReview.
\newline Once created, an AntReview is available to be fulfilled by Peer-Reviewers, uploading the peer-review on IPFS before the deadline.
\newline The AntReview after being validated is then accepted by the Issuer and paid equally between Peer-Reviewers.
\newline Also, the Issuer can cancel the AntReview at any time and withdraw the amount of ether staked.
\newline One of the key aspects of the protocol is the concept of Proof of Existence, introduced by Stuart Haber \& W. Scott Stornetta with the paper "How to time-stamp a digital document"\cite{TimeStamp-Haber}
\newline As the pioneers of blockchain an cited by Bitcoin whitepaper, they were in a mission to solve the problem of immutability of digital records that became reality with the Blockchain and Bitcoin\cite{Bitcoin} as its first application.
\newline In Ethereum \cite{Ethereum} the concept of immutability is achieved via the blockchain and proof of work consesus algorithm by a chain of timestamped block hashes that are secured by miners competing computations.
\newline AntsReview is evaluating the advantages of storing the hashes of the peer-reviews into a Merkle Tree \cite{BayerHaber1992} to achieve immutability and efficiency in verifying the data with a complexity of O(logn) for searching through the tree.
\newline A Merkle tree is a particular type of binary tree, formed by a set of nodes with a large set of leaf nodes at the bottom of the tree containing representing the hash of the original data, a set of intermediate nodes where each node is the sum of the two children hashes, ending with a single root hash.
\newline In order to verify if a specific hash is included into a Merkle Tree, leveraging on MerkleProof.sol by OpenZeppelin Library, we need to provide a proof, generated from the leaf of interest, that represent the remification derived from the leaf, the root hash and finally the leaf we want to verify.
\newline The paper and peer-review documents will be included into a Merkle Tree by hashing the data using keccak256, a cryptographic hashing algorithm available in Solidity \cite{Solidity}, an object-oriented programming language for writing smart contracts that run on the Ethereum Virtual Machine (EVM).

@@

 Externally Owned Accounts (EOA) in Ethereum are controlled by private keys, are 20 bytes long and have no code. An user can send messages from an externally owned account by creating and signing a transaction.
\newline The limitation of such solution regarding the Privacy of the Protocol is due to the fact that blockchain and transactions are public so anyone can see the details of a transaction, browsing a block explorer like Etherscan, and also they're subjected to data mining to extract value and identify users in the blockchain.
\newline To avoid that, AntsReview will implement zkAnt, an Ant token wrapped into AZTEC Protocol, where leveraging on zkSNARKS, and PLONK in the future, will allow private transactions in the system to maintain the privacy and anonimity of Peer-Reviewers.
\newline The AZTEC Protocol was conceived to enable privacy on public blockchains. It uses ZK-SNARKS to validate encrypted transactions.
\newline ZK-SNARKs (Zero-Knowledge Succinct Non-Interactive Argument of Knowledge) \cite{ZKSNARKs} refers to a proof construction where one can prove possession of certain information, like a secret key, without revealing that information, and without any interaction between prover and verifier.
\newline Zero-Knowledge \cite{ZeroKnoledge} proofs allow an actor (prover) to prove to another (verifier) that a statement is true, without revealing any information apart from the validity of the statement itself.
\newline Future developments will investigate viable solutions, for scaling the system, like ZK-Rollups by AZTEC Protocol, one of the options being developed for a type of layer 2 construction that runs on top of Ethereum to improve scalability. This will enable to run smart contracts at scale with quasi-instant transactions while still being secured by Ethereum.
\subsubsection{Privacy/anonymity}. To enhance the peer-reviewer's privacy, we would like to implement zkANT, an ERC20 token, Ant, wrapped into AZTEC Protocol ZK-SNARKs, a non-interactive type of zero-knowledge privacy protocol to enable private transactions on Ethereum. Zero-knowledge proof is a mathematical cryptographic method that through values permutations allows one party (the prover) to prove to another (the verifier) the veracity of a statement, without having to reveal what the statement is. We will use ZK-SNARKs (which stands for “Zero-Knowledge Succinct Non-Interactive Argument of Knowledge”) via the open source libraries of AZTEC protocol. AZTEC, now TURBOPLONK bla bla (faster?) combines the confidentiality of the transactions (the value of the transaction is hidden, the amount of token (?) is not revealed thus preventing biases in the peer-review quadratic voting process = "I want to bet on this review because I want to win the bounty") with general-purpose computation (it's a Turing-complete Virtual Machine): this means transaction are not limited just to the local cryptocurrency (in our case ANT) but cross-asset trades are allowed (I can exchange ANT tokesn with other crypto-currencies).
\section{Discussions}
\subsection{A new community-driven standard?}
- a change is already happening: specially new born publishers are opening up review process (BioMed Central, ELife, Frontiers, PeerJ, F1000 Research) -- from 2020 also Nature declared that will do the same.

>>>>

\begin{document}
%
\title{Ants-Review: A Protocol For Open Anonymous Peer-Reviews}
%
%\titlerunning{Abbreviated paper title}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{Bianca Trovò\inst{1,2}\orcidID{0000-0002-6776-2304}\thanks{Correspondent author: bianca.trovo@alumni.unitn.it} \and
Nazzareno Massari\inst{3,4}\orcidID{0000-0002-6638-2174}}
%
\authorrunning{B. Trovò et N. Massari}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{Sorbonne Université, Faculté des Sciences et Ingénierie, 75005 Paris, France \and
Neurospin research center, CEA/SAC/DSV/I2BM, 91191 Gif-sur-Yvette, France
\email{bianca.trovo@alumni.unitn.it}\\
\and
Alma Mater Politecnico di Torino, 10129 Turin, Italy\and
Independent Blockchain Engineer, London, UK \\
\email{nazzareno@nazzarenomassari.com}}
%
\maketitle              % typeset the header of the contribution
%
\begin{abstract}
Peer-review is a necessary and essential quality control step for scientific publications. However, the process, which is very costly in terms of time investment, not only is not remunerated but it’s also not recognized by the academic community as a relevant scientific output for a researcher. Therefore, scientific dissemination is affected. Here, to solve this issue we propose a blockchain-based incentive protocol that rewards scientists also for their contributions to other scientists’ work and that builds up a reputational system. We designed a basic Bounty-like contract called AntsReview that allows any author to issue a call for peer-reviewing their scientific publication. If requirements are met, peer-reviews will be audited by an external editor and payed by the Issuer. To promote ethical behaviour the system will implement a quadratic funding on AntsReview.
\keywords{Blockchain  \and Open Science \and Peer-review \and Incentivization.}
\end{abstract}
%
%
\section{Introduction}
From its birth in 2008 as a distributed ledger for the peer-to-peer electronic cash system Bitcoin \cite{Bitcoin}, blockchain technologies (BCTs) have spread far beyond the sole cryptocurrency domain, in particular after the implementation of a general purpose smart contract functionality introduced by Ethereum \cite{Ethereum-Wood}.
Besides a growing number of applications ranging from business, healthcare, music industry, government, identity to cite but a few, blockchain technology has recently started to catalyse the attention of the scientific community as well \cite{Bitcoin-Nature-focus,vanRossum2017-DigSci} with the promising potential of being a 'game changer' in outdated and broken scientific practices and leading towards Open Science \cite{AES}. In particular, a 'blockchainified science'\cite{BlockchainforScience} could 'reduce waste'\cite{ReducingWaste-Lancet}, by disclosing each step the research cycle to 'scientific self-correction' way before the final publication step and therefore help fixing the current reproducibility crisis in science. Finally, scholars have pointed out how the intrinsic characteristics of blockchain technology (decentralization, for which there are no trusted third parties; cryptographic hashing and timestamping, that create a digital footprint able to keep a traceable chronological record of research objects; immutability or append-only, for which data cannot be altered or retrieved) set the basis for a open science infrastructure \cite{ReviewBlockchain2019} where decisional processes are transparent and therefore more democratically accessible to all the stakeholders (researchers, reviewers, funders, taxpayers).
A thorny issue in the academic system that can be tackled by blockchain concerns the status and accreditation of peer-review, the core process of scientific validation currently facing a crisis. In this paper we propose a solution to the problem of reviewers recognition based on the principles of token economy.

@@

@@

AntsReviewRoles[\ref{appendix:a}], to ensure integrity of the system, implements an access management, leveraging on AccessControl.sol by OpenZeppelin Library \cite{OZ}, through the creation of the Roles Issuer and Peer-Reviewer.
\newline It also integrates a circuit breaker design pattern via Pausable.sol by OpenZeppelin to allow the Pauser Role, that by default is the Owner of the Smart Contracts, to pause (or unpause) the functions in case of emergency.
\newline In this way, only the Issuer (author) can create a new AntReview.
\newline Once created, an AntReview is available to be fulfilled by Peer-Reviewers, uploading the peer-review on IPFS before the deadline.
\newline The AntReview after being validated is then accepted by the Issuer and paid equally between Peer-Reviewers.
\newline Also, the Issuer can cancel the AntReview at any time and withdraw the amount of ether staked.
\newline One of the key aspects of the protocol is the concept of Proof of Existence, introduced by Stuart Haber \& W. Scott Stornetta with the paper "How to time-stamp a digital document"\cite{TimeStamp-Haber}
\newline As the pioneers of blockchain an cited by Bitcoin whitepaper, they were in a mission to solve the problem of immutability of digital records that became reality with the Blockchain and Bitcoin \cite{Bitcoin} as its first application.
\newline In Ethereum \cite{Ethereum} the concept of immutability is achieved via the blockchain and proof of work consesus algorithm by a chain of timestamped block hashes that are secured by miners competing computations.
\newline AntsReview is evaluating the advantages of storing the hashes of the peer-reviews into a Merkle Tree \cite{BayerHaber1992} to achieve immutability and efficiency in verifying the data with a complexity of O(logn) for searching through the tree.
\newline A Merkle tree is a particular type of binary tree, formed by a set of nodes with a large set of leaf nodes at the bottom of the tree containing representing the hash of the original data, a set of intermediate nodes where each node is the sum of the two children hashes, ending with a single root hash.
\newline In order to verify if a specific hash is included into a Merkle Tree, leveraging on MerkleProof.sol by OpenZeppelin Library, we need to provide a proof, generated from the leaf of interest, that represent the remification derived from the leaf, the root hash and finally the leaf we want to verify.
\newline The paper and peer-review documents will be included into a Merkle Tree by hashing the data using keccak256, a cryptographic hashing algorithm available in Solidity \cite{Solidity}, an object-oriented programming language for writing smart contracts that run on the Ethereum Virtual Machine (EVM).

@@

 Externally Owned Accounts (EOA) in Ethereum are controlled by private keys, are 20 bytes long and have no code. An user can send messages from an externally owned account by creating and signing a transaction.
\newline The limitation of such solution regarding the Privacy of the Protocol is due to the fact that blockchain and transactions are public so anyone can see the details of a transaction, browsing a block explorer like Etherscan, and also they're subjected to data mining to extract value and identify users in the blockchain.
\newline To avoid that, AntsReview will implement zkAnt, an Ant token wrapped into AZTEC Protocol, where leveraging on zkSNARKS, and PLONK in the future, will allow private transactions in the system to maintain the privacy and anonimity of Peer-Reviewers.
\newline The AZTEC Protocol was conceived to enable privacy on public blockchains. It uses a series of zero-knowledge proofs (ZK-SNARKs) and homomorphic encryption to validate encrypted transactions.
\newline ZK-SNARKs (Zero-Knowledge Succinct Non-Interactive Argument of Knowledge) \cite{ZKSNARKs} refers to a proof construction where one can prove possession of certain information, like a secret key, without revealing that information, and without any interaction between prover and verifier.
\newline Zero-Knowledge \cite{ZeroKnoledge} proof is a mathematical cryptographic method that through values permutations allow one party (the prover) to prove to another (the verifier) the validity of a statement, without revealing the statement itself.
\newline Future developments will investigate viable solutions, for scaling the system, like ZK-Rollups by AZTEC Protocol, one of the options being developed for a type of layer 2 construction that runs on top of Ethereum to improve scalability. This will enable to run smart contracts at scale with quasi-instant transactions while still being secured by Ethereum.

\section{Discussions}
\subsection{A new community-driven standard?}
- a change is already happening: specially new born publishers are opening up review process (BioMed Central, ELife, Frontiers, PeerJ, F1000 Research) -- from 2020 also Nature declared that will do the same.
